\documentclass[11pt]{article}
\usepackage{lmodern}
\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}
\usepackage[letterpaper]{geometry}
\geometry{verbose,tmargin=1.5cm,bmargin=1.5cm,lmargin=1.5cm,rmargin=1.5cm}
%\usepackage{fancyhdr}
%\pagestyle{fancy}
\setlength{\parskip}{\smallskipamount}
\setlength{\parindent}{0pt}
\usepackage{color}
%\usepackage{babel}
\usepackage{fontawesome}
\usepackage{array}
\usepackage{longtable}
\usepackage{amssymb}
\usepackage[authoryear]{natbib}

% Hide or show money
\usepackage{comment}
\newif\ifshow
%\showfalse
\showtrue
\ifshow
    \includecomment{money}
\else
    \excludecomment{money}
\fi


% Change some distances in bibliography:
    \setlength{\bibsep}{3pt}
    \setlength{\bibhang}{7pt}
\usepackage[unicode=true,pdfusetitle,
 bookmarks=false,
 breaklinks=true,pdfborder={0 0 0},pdfborderstyle={},backref=false,colorlinks=true]
 {hyperref}
\hypersetup{urlcolor=blue}
\usepackage{breakurl}
%Tweaking lists:
\usepackage{enumitem}

\usepackage{lastpage}
%\headsep 10pt
\definecolor{blue}{RGB}{12, 8, 129}
% \usepackage{titlesec}

\begin{document}

\begin{center}
\Large \sc Jacopo Mazza \hfill Utrecht University, School of Economics \\
\end{center}
\vspace{-.3cm}
\noindent\rule{\textwidth}{1pt}
\parbox[t]{.45\textwidth}{\begin{flushleft}
    \vspace{-.5cm}
    \begin{footnotesize}
    \href{https://jacopoto.github.io/}{\faGlobe\enspace Website} \\
    \href{github.com/jacopoto} {\faGithub\enspace jacopoto} \\
    \href{mailto:j.mazza@uu.nl}{\faEnvelopeO\enspace j.mazza@uu.nl} \\
%    \href{\faGithub\enspace github.com/jacopoto} \\
    \vspace{.35cm}
    Last updated on: \today \\
    \end{footnotesize}
\end{flushleft}} \hfill
\parbox[t]{.45\textwidth}{\begin{flushright}
    \begin{footnotesize}
    \vspace{-.5cm}
    Utrecht School of Economics \\
    Adam Smith Hall, \\
    Kriekenpitplein 21-22, \\
    3584 EC Utrecht, \\
    The Netherlands \\
    \end{footnotesize}
\end{flushright}} \\
\noindent\rule{\textwidth}{1pt}

\subsection*{\sc Employment}

\hspace{20pt}\textbf{Utrecht University, Utrecht (The Netherlands)}\\
\hspace*{27pt}Assistant Professor, School of Economics \emph{(2022\textendash)}\\
\hspace*{20pt}\textbf{European Commission, Joint Research Centre}\\
\hspace*{27pt}Scientific Officer, Knowledge Centre for Migration and Demography \emph{(2018\textendash2022)}\\
\hspace*{20pt}\textbf{University of Essex, Colchester (U.K.)}\\
\hspace*{27pt}Lecturer, Department of Economics \emph{(2016\textendash2018)}\\
\hspace*{20pt}\textbf{University of Manchester, Manchester (U.K.)}\\
\hspace*{27pt}Lecturer, Department of Economics \emph{(2012\textendash2016)}

\subsection*{\sc Other Affiliations}
\hspace{20pt}\textbf{University of Essex, Colchester (U.K.)}\\
\hspace*{27pt}Research Associate, Department of Economics \emph{(2019\textendash )}

\subsection*{\sc Education}

\hspace*{20pt}\textbf{Ph.D. University of Amsterdam}, Economics, \emph{(2012)} \\
\hspace*{20pt}\textbf{M.Sc. University of Amsterdam}, Economics,  \emph{(2006)} \\
\hspace*{20pt}\textbf{Laurea Bocconi University}, Economics, \emph{ (2004)}

\subsection*{\sc Journal publications}

\nocite{mazza_scipioni_jepp}
\nocite{bicakova_cortes_mazza_ej}
\nocite{mazza_vohpem_hartog_le}
\nocite{mazza_vophem_jrssa}

\hspace*{20pt}%
\begin{minipage}[t]{0.9\textwidth}%
\vspace{-.9cm}
    \centering
    \renewcommand\refname{}
        \bibliographystyle{ecta_YEAR}
        \bibliography{my_pubs}
\end{minipage}

\vspace{-.3cm}

\subsection*{\sc Working papers}

\begin{itemize}[itemsep=0pt, leftmargin=20pt]
\item [-]{Make Your Own Luck: The Wage Gains from Starting College in a Bad Economy}\\
\emph{with Alena Bi\v{c}\'{a}kov\'{a} and Matias Cortes}
\item [-]The Fiscal Impact of Immigration in the EU\\
\emph{with Michael Christl, Alain Bélanger, Alessandra Conte and Edlira Narazani} (\textbf{R\&R at Fiscal Studies}) \\
JRC Working Papers on Taxation and Structural Reforms No 01/2021; GLO Discussion Paper, No. 814.
\item [-]Being on the Frontline? Immigrant Workers in Europe and the COVID-19 Pandemic\\
\emph{with Francesco Fasani} (\textbf{R\&R at ILR Review})\\
CEPR Discussion Paper 15590; CReAM Discussion Paper 01/21; IZA Discussion Paper 13963; Queen Mary University Working Paper 918.
\item [-]Educational Choice, Initial Wage, and Wage Growth\\
\emph{with Hans van Ophem}\\
Tinbergen Institute Discussion Paper 2020-030/III
\item [-]Does Risk Matter? A Semiparametric Model for Educational Choices in the Presence of Uncertainty \\
University of Manchester Working Paper 1225

\end{itemize}

\subsection*{\sc Work in progress}

\begin{itemize}[itemsep=0pt, leftmargin=20pt]
\item [-]{The Wage Effects of Grade Inflation in College}\\
\emph{with Peter Backus and Arnaud Chevalier}
\item [-]College Participation Over the Business Cycle: Composition and Behavioral Changes\\
\emph{with Alena Bi\v{c}\'{a}kov\'{a}, Matias Cortes, Kelly Foley and Peter McHenry}
\item [-]{The Long Run Effects of Migration Exposure on Attitudes Towards Migration}\\
\emph{with Mariapia Mendola and Marco Scipioni}
%\item [-]When intentions matter\textendash identifying the prevalence and source of poor-quality inputs in Kenya\\
%\emph{with Jose Clavijo and Travis Lybbert}
%\item[-] Income Volatility and Technology Choice \\
%\textit{with Rachel Hern\'{a}ndez  Frattarola}
\end{itemize}

\subsection*{\sc Other publications \& reports}

\begin{itemize}[itemsep=0pt, leftmargin=20pt]
\item [-]B\'elanger, A., M. Christl, A. Conte, J. Mazza and E. Narazani, 2020. {``Projecting the net fiscal impact of immigration in the EU.''}
European Commission, JRC\textendash EUR 30407.
\item [-]Fasani, F. and J. Mazza, 2020. {``A Vulnerable Workforce: Migrant Workers in the COVID-19 Pandemic.''}
European Commission, JRC\textendash EUR 30225.
\item [-]Fasani, F. and J. Mazza. 2020, {``Immigrant Key Workers: Their Contribution to Europe's COVID-19 Response.''} IZA Policy Paper No. 155.
\item [-]Di Pietro, G., F. Biagi, P. Costa, Z. Karpinski and J. Mazza, 2020. {``The likely impact of COVID-19 on education: Reflections based on the existing literature and recent international datasets''}. JRC Working Papers JRC121071.
\item [-]Mazza, J., 2019. ``{The Effect of Non-Native Pupils on Natives' Learning: Evidence from the EU}.''
J.R.C. Technical Report, Publication Office of the European Union.
\item [-]Conte, A. and J. Mazza, 2019. ``{Migrants and Welfare Dependency: Evidence from the EU}.''
J.R.C. Technical Report, Publication Office of the European Union
\item [-]Biagi, F., S. Grubanov-Boskovic and J. Mazza,
2019. ``Over-education of migrants: Evidence from the EU'' J.R.C. Technical Report, Publication Office of the European Union
\item [-]Sulla, V., R. Munoz Moreno, C. Da Maia, L. Klapper, P. Van Oudheusden, M. U. Guven, J. Mazza, D. Nikitin, V. Polodoo, P. L. Randriankolona and T. E. Heleniak, 2016.
``{Mauritius \textendash Inclusiveness of growth and shared prosperity}.'' World Bank WP 90006.

\end{itemize}

\subsection*{\sc Grants }

\begin{itemize}[itemsep=0pt, leftmargin=20pt]
\item [-]2016-2018: The British Academy Small Grant \#R119450
\begin{money}
(\pounds10,000)
\end{money}
with Matias Cortes \\
\emph{Caught in the cycle: the long term consequences of college major selection in a recession}

\end{itemize}

%\subsection*{\sc Awards \& Fellowships}

%\begin{itemize}[itemsep=-.1cm, leftmargin=20pt]
%\item [-]Association for Public Policy Analysis and Management, 40 for 40 Fellowship, 2018
%\item [-]Taylor Hibbard award for Excellence in Graduate Teaching, 2018 (based on student vote)
%\item [-]Gordon A. King Best Dissertation Award, UC Davis Agricultural \& Resource Economics (2015)
%\item [-]Henry A. Jastro Graduate Research Fellowship, UC Davis (2012-2013)
%\item [-]Departmental Fellowship, Agricultural and Resource Economics, UC Davis (2009-2010)
%\item [-]Phi Beta Kappa, Colby College (2016)
%\end{itemize}

\subsection*{\sc Invited seminars \& panels}
\textit{Planned indicated with *}
\begin{itemize}[itemsep=.9pt, leftmargin=20pt]
    \item[]\textbf{2021:} Centro Studi Luca D'Agliano: 5th Annual Conference; DG EMPL\textendash European Commission; Jean Monnet Workshop\textendash University of Pisa; Central Bank of Romania.
    \item[]\textbf{2020:} Migration Policy Institute.
    \item[]\textbf{2017:} University of Utrecht (Economics); University of the Balearic Islands (Economics).
    \item[]\textbf{2013:} Institute for Fiscal Studies.
    \item[]\textbf{2012:} CERGE-EI - Prague (Economics); Ludwig Maximilians University, M\"unich (Economics).

\end{itemize}

\subsection*{\sc Conferences \& workshops}
\begin{itemize}[itemsep=.9pt, leftmargin=20pt]
    \item[]\textbf{2022:} EEA-ESEM Congress.
    \item[]\textbf{2019:} ZEW workshop on the Economics of Higher Education; 24th Annual SOLE Meeting.
    \item[]\textbf{2018:} 30th EALE Conference; Royal Economic Society Conference.
    \item[]\textbf{2015:} SOLE/EALE World Conference.
    \item[]\textbf{2013:} Royal Economic Society Conference.
    \item[]\textbf{2011:} Tinbergen Institute - Amsterdam; 4th Italian Congress of Econometrics and Empirical Economics.
    \item[]\textbf{2010:} IX “Brucchi Luchino” Labour Economics Workshop, University of Padua.
    \item[]\textbf{2008:} 20th EALE Conference.
    \item[]\textbf{2005:} ASSA meeting.
\end{itemize}

\subsection*{\sc Media Coverage}
{\emph{BBC; The Guardian; Newsweek; Il Corriere della Sera; La Repubblica; Algmeen Dagblad; De Pers; Rtl 4; The Times Higher Education}.

\subsection*{\sc Work experience}
\begin{itemize}[leftmargin=20pt]
    \itemsep-.1cm
    \item[] Consultant, The World Bank (2014)
    \item[] Intern, Central Planning Bureau\textendash The Hague, The Netherlands (2006)
\end{itemize}

\subsection*{\sc Teaching}
\begin{itemize}[leftmargin=20pt]
    \itemsep0cm
    \item[-]\textbf{University of Essex, Department of Economics}
    \itemsep-.1cm
    \item[] Applied Econometrics. Ph.D. level. 2018
    \item[] Labour Economics. Undergraduate level. 2017, 2018
    \item[] Economics for Business. Undergraduate level. 2016, 2017
    \itemsep.1cm
    \item[-]\textbf{University of Manchester, Department of Economics}
    \itemsep-.1cm
    \item[] Introduction to Econometrics. Master level. 2013, 2014, 2015
    \item[] Further Econometrics. Master level. 2013
    \item[] Labour Economics. Undergraduate level. 2012, 2013, 2014, 2015
    \item[] Introduction to Statistics. 2013
    \itemsep.1cm
    \item[-]\textbf{University of Amsterdam, Department of Economics and Business}
    \itemsep-.10cm
    \item[] Labour Economics. Undergraduate level. 2009

\end{itemize}

%\subsection*{\sc Advising}

%\begin{itemize}[leftmargin=20pt]
%    \itemsep-.1cm
%    \item[] Rachel Frattarola, PhD AAE (2018) Dissertation committee member
%    \item[] Justin Delorit, PhD Civil \& Environmental Engineering (2018) Dissertation committee member
%    \item[] Norihiko Matsuda, PhD AAE (2018) Dissertation committee member
%    \item[] Jessica Zhu, PhD AAE (2019) Dissertation committee member
%    \item[]	Jens Engelmann, PhD AAE (2019) Dissertation committee member
%    \item[] Naoki Nishimura, PhD AAE, Dissertation committee member
%    \item[]	Evan Morier, PhD Political Science, Dissertation committee member
%    \item[]	Joshua Deutschmann, PhD AAE Dissertation committee member
%    \item[]	Eduardo Cenci, PhD AAE, Dissertation committee member
%\end{itemize}


\subsection*{\sc University service}
\begin{itemize}[leftmargin=20pt]
    \itemsep-.1cm
    \item[] Econometrics \& Applied Economics workshop coordinator, Department of Economics, University of Manchester (2012\textendash 2016)
    \item[] Brownbag workshop coordinator, Department of Economics and Business, University of Amsterdam (2007\textendash 2010)
\end{itemize}

\subsection*{\sc Outside service}

\begin{itemize}[itemsep=.9pt, leftmargin=20pt]
    \item[]\textbf{Journal refereeing:} American Economic Journal: Economic Policy; The Economic Journal; European Economic Review; Labour Economics; Regional Science and Urban Economics; Oxford Economic Papers; The B.E. Journal of Economic Analysis and Policy; The Manchester School.
\end{itemize}

\subsection*{\sc Other information}
\begin{itemize}[itemsep=.9pt, leftmargin=20pt]
    \item[]\textbf{Languages:} Italian (Native), English (Fluent), French, Spanish (Proficient), Dutch (Basic).
%    \item[]\textbf{Associations:} American Economic Association, Agricultural and Applied Economics Association, Economic Science Association, Australasian Agricultural and Natural Resource Association
\end{itemize}

\end{document}
